Considering scale in multilayer animal social networks

### 2020-06-26 paper/manuscript.Rmd
n =

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). Given the observed trend of these multilayer metrics
decreasing in variance after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

>>>>

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). <!--TODO double check-->Since the variance in these 
multilayer metrics decreases after a certain number
of observations, this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing social dynamics
across contexts.
